---
title: "Data Analysis (Mechatronics and Robotics Concept Inventory)"
output:
  
  html_document: default
  pdf_document: default
  word_document: 
    fig_width: 6.5
    fig_height: 4

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

```{r, echo=FALSE, message=FALSE}
library(dplyr)
library(data.table)
library(knitr)
require(likert)
opts_knit$set(global.par=TRUE)
```

```{r}
T <- read.csv("Responses.csv", stringsAsFactors = FALSE)
#replace blank elements with NA
for (i in names(T)) {
    T[[i]][T[[i]] == ""] = NA
}
```

```{r}
#there are two responses which indicated both Academic and Industry, so they are
#classified one as Industry and one as Academic as shown below. The person classified as industry is
#an adjunct faculty member with industry experience. The other indicates a teaching and research position,
#so it's not clear what to do with this one.
T$role[T$role == "Academic Administrator"] = "Academic"
T$role[T$role == "Faculty, 50/50 research and teaching"] = "Academic"
T$role[T$role == "Faculty, primary focus is research"] = "Academic"
T$role[T$role == "Faculty, primary focus is research, Faculty, 50/50 research and teaching"] = "Academic"
T$role[T$role == "Faculty, primary focus is research, Faculty, primary focus is teaching, Faculty, 50/50 research and teaching"] = "Academic"
T$role[T$role == "Faculty, primary focus is teaching"] = "Academic"
T$role[T$role == "Faculty, 50/50 research and teaching, Industry"] = "Academic"
T$role[T$role == "Faculty, primary focus is teaching, Industry, only adjunct faculty"] = "Industry"
T$role[T$role == "Industry, Alumni"] = "Industry"
T$role[T$role == "Industry, Student (graduate)"] = "Industry"
T$role[T$role == "Researcher at a Research Center which is not a university (TNO)"] = "Industry"
T$role[T$role == "Staff 50/50 teaching and maintaining lab. "] = "Academic"
T$role[T$role == "Student (graduate)"] = "Student (G)"
T$role[T$role == "Student (undergraduate)"] = "Student (UG)"
T$role = factor(T$role) #extract factors
```

```{r}
#convert expertise to an integer-valued factor label
T$expertise <- factor(T$expertise, levels = c("Mechatronics and Robotics", "Mechatronics", "Robotics", "Neither Mechatronics nor Robotics"))

#convert date
#T$timestamp <- as.POSIXct(T$timestamp, format = "%m/%d/%Y %H:%M")

#convert engineering science question to nuemric data
T$escience <- factor(T$escience, levels = c("Strongly Disagree", "Somewhat Disagree", "Neutral", "Somewhat Agree", "Strongly Agree"))
```

```{r}
#convert characters to integer-coded factors using the defined levels
cols = names(T)
for (i in cols[5:238]) {
    T[[paste(i)]] <- factor(T[[paste(i)]], levels = c("1 - Not Relevant", "2 - Unimportant", "3 - Neutral", "4 - Important", "5 - Extremely Important"))
}


T <- data.table(T)
```

# How do people feel about emphasizing computational techniques?

The mean response of undergraduate students is significantly different from the baseline case of academics. There were no significant differences found between Academic and Industry responses or between Academic and Graduate Student responses.
```{r}
summary(lm(data = T, formula = as.double(escience) ~ role, na.action = na.omit))
```
Graphically depicted as stacked bar charts:

```{r fig-escience, fig.width=8, fig.height=3}
escience <- T[,4]
names(escience)=c("Engineering Science - Computational Techniques")
likert_escience = likert(items=escience, grouping=T$role)

likert.bar.plot(likert_escience, center=3) + ggtitle("Engineering Science") + theme_classic() + theme(plot.margin=unit(c(0.5,0.5,0.5,0.5),"cm"))

```

# Importance - Basic science courses

```{r fig-basic-courses, fig.width=9, fig.height=2}
course_items <- T[,5:9]
names(course_items) <- c("Chemistry","Physics - Mechanics","Physics - Electromagnetics","Physics - Optics","Physics - Quantum Mechanics")
course_basic <- likert(course_items)
likert.bar.plot(course_basic, center=3) + ggtitle("Science Courses") + theme_classic() + theme(plot.margin=unit(c(0,0,0,0),"cm"))
```

# Importance - Basic math courses

```{r fig-basic-math, fig.width=9, fig.height=3}
course_items <- T[,10:18]
names(course_items) = c("Single Variable Calculus","Multivariate Calculus","Ordinary Differential Equations","Partial Differential Equations","Linear Algebra","Numerical Methods","Complex Analysis","Statistics","Discrete Mathematics")
course_math <- likert(course_items)
likert.bar.plot(course_math, center=3) + ggtitle("Math Courses") + theme_classic() + theme(plot.margin=unit(c(0,0,0,0),"cm"))
```

# Importance - Engineering 1 
```{r fig-eng1, fig.width=9, fig.height=3.5}
course_items <- T[,19:30]
names(course_items) <- c("Engineering Economics","Engineering Graphics","Statics","Dynamics","Kinematics","Strength of Materials","Machine Design","Material Science","Thermodynamics","Heat Transfer","Fluid Mechanics","Actuators")
course_eng1 <- likert(course_items)
likert.bar.plot(course_eng1, center=3) + ggtitle("Engineering 1 Courses") + theme_classic() + theme(plot.margin=unit(c(0,0,0,0),"cm"))
```

# Importance - Engineering 2
```{r fig-eng2, fig.width=9, fig.height=3}
course_items <- T[,31:39]
names(course_items) <- c("Dynamic Systems","Control Systems","Instrumentation","Sensor Design","AI and Machine Learning","Machine Vision","Signals and Systems","Communication Systems","Embedded Systems")
course_eng2 <- likert(course_items)
likert.bar.plot(course_eng2, center=3) + ggtitle("Engineering 2 Courses") + theme_classic() + theme(plot.margin=unit(c(0,0,0,0),"cm"))
```

# Importance - Engineering 3
```{r fig-eng3, fig.width=9, fig.height=4.5}
course_items <- T[,40:58]
names(course_items) <- c("Programmable Logic Controllers","Procedural Programming","Object-oriented Programming","Hardware Description Languages","Data Structures","Complexity Analysis","Computer Architecture","Formal Languages & Automata Theory","Operating Systems","DC Circuits","AC Circuits","Analog Electronics","Digital Electronics","Power Electronics","Semiconductor Materials and Devices","Electric Machines","Electromagnetics","Real-Time Programming","Networking")
course_eng3 <- likert(course_items)
likert.bar.plot(course_eng3, center=3) + ggtitle("Engineering 3 Courses") + theme_classic() + theme(plot.margin=unit(c(0,0,0,0),"cm"))
```

# What are the top and bottom ranked concepts?

```{r figs-concept-rankings, fig.width=11, fig.height=4}
all_topics <- T[,59:238]
names(all_topics) <- c("Atomic structure","Periodic table","Chemical bonding","Stoichiometry","Gas laws","Intermolecular forces","Newton's laws of motion","Gravity","Fixed-axis rotations","Conservation of energy","Conservation of momentum","Harmonic oscillation","Collisions","Impulse-momentum principle","Work-energy principle","Electric and magnetic fields","Dielectric materials","Magnetic materials","Circuits","Faraday's law","Lorentz force","Maxwell's equations","Refraction","Interference","Diffraction","Imaging","Limits","Derivatives","Integrals","Three-dimensional analytic geometry","Partial derivatives","Multiple integrals","Gauss' theorem","Stokes' theorem","Linear and nonlinear differential equations","Laplace transform","First-order equations","Second-order equations","State-space systems","Heat equation","Wave equation","Laplace's equation","Green's functions","Systems of linear equations","Row reduction, Echelon forms","Gram-Schmidt","Matrix operations, Matrix inverse","Block matrices","Linear dependence, Linear independence","Subspaces, bases, and dimensions","Orthogonal bases, projections","Determinants","Eigenvalues and eigenvectors","Diagnolization","Special matrices - symmetric, positive definite, etc","Similar matrices","Linear transformations","Singular value decomposition","Series expansion","Root-finding - Newton-Raphson, binary search, etc","Integration, Runge-Kutta","Interpolation","Fast Fourier transfrom","Least squares","Principal component analysis","Partial differential equations - finite element method","Complex numbers","Analytic functions","Complex integrals","Complex series","Residues and poles","Probability","Probability density functions","Moments","Hypothesis testing","Net present value","Future worth","Rate of return","Breakeven analysis","Amortization","Depreciation","Financial projections","Sectional views","Dimensioning and tolerancing","Assemblies","Parametric solid modeling","Statically determinate equilibirum","Center of gravity","Friction","Stress & Strain","Statically indeterminate problems","Torsion","Bending","Particle kinematics","Particle kinetics","Rigid body kinematics","Rigid body kinetics","3D dynamics - numerical","Constraints","Gears","Cams","Serial mechanisms","Parallel mechanisms","Machinery","Forward kinematics","Inverse kinematics","Stress analysis","Deflection and stiffness","Static loading","Dynamic loading and fatigue","Fasteners","Welded joints","Springs","Bearings","Clutches","Brakes","Belts and pulleys","Measurement theory","Error estimation","Error propogation","Instrumentation specifications","Data acquisition","Signal conditioning","Handling digital data","Phases and phase diagrams","Metals and alloys","Engineering material selection","Plastics","Rubbers","Ceramics","Control volumes","Properties of substances","Work and heat","1st and 2nd laws of thermodynamics","Power and refrigeration cycles","Water-vapor mixtures","Combustion","Conduction","Radiation","Convection","Fluid statics, kinematics, and dynamics","Conservation laws","Integral analysis (Fluids)","Differential analysis and similarity","Internal and external viscous flows","Compressible flows and drag","LTI systems","Analogies between energy domains","Multi-energy domain systems","Causal models","Block diagrams","Acausal models, differential algebraic systems","Vibration","Continuous and discrete time systems (Controls)","Feedback control","Stability criteria","Frequency response","Frequency domain compensation","PID control","Filtering and filter design","Fourier transform","Modulation","Sampling theory","Serial vs parallel communication","Asynchronous serial communication","Synchronous ommunication","Continuous and discrete time systems (Signals & Systems)","Regression analysis","Classification methods","Dimensionality reduction","Clustering","Reinforcement learning","Supervised learning","Image models","Feature extraction","Camera calibration","Stereo vision","Photogrammetry","Motion detection and object tracking","Biomedical imaging")
lall_topics <- likert(all_topics)

df <- lall_topics$results
ii <- order(df$`5 - Extremely Important` + df$`4 - Important`, decreasing=TRUE)

ordered_results <- df[ii,]

top_results <- ordered_results[1:10,]
top_results$Item <- factor(top_results$Item)
bottom_results <- ordered_results[(nrow(ordered_results)-9):nrow(ordered_results),]
bottom_results$Item <- factor(bottom_results$Item)


likert.bar.plot(likert(summary = top_results), center=3, ordered=TRUE) + ggtitle("Top results") + theme_classic() 
likert.bar.plot(likert(summary = bottom_results), center=3, ordered=TRUE) + ggtitle("Bottom results") + theme_classic()
```
```{r fig-all-concepts, fig.width=11, fig.height=35}
par(mai=c(0.5,5,0.5,2))
likert.bar.plot(lall_topics, center=3, ordered=TRUE,wrap=200) + ggtitle("All topics") + theme_classic() + theme(axis.text.y = element_text(hjust=1,size=10))
```
